13th International Satisfiability Modulo Theories Competition (SMT-COMP 2018): Rules and Procedures

### 2018-04-17 rules/rules18.tex
add vampire reference
Update principal changes; first public version for 2018 (still draft)

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Matthias Heizmann, Albert Oliveras, Giles Reger, Aaron Stump, and
  Tjark Weber.}  describes the rules and competition procedures for
SMT-COMP~2018.  The principal changes from the previous competition
rules are the following: \rem{Aina: All of this bullets are not new in
  2018 anymore, maybe move them elsewhere? This information should not
  be lost.}
\begin{itemize}
\item Submission of accompanying information for solvers is via a web
  form (rather than by email to the organizers).  \emph{Rationale:}
  Email submissions were often incomplete, leading to ambiguity and
  further inquiries.  The form provides a more structured way of
  submitting information.
\item Benchmarks will use (a subset of) version~2.6 of the SMT-LIB
  language.  \emph{Rationale:} This is the latest version of the
  SMT-LIB language.  It is largely backwards-compatible with earlier
  versions (in particular~2.0 and~2.5).
\item Benchmarks that use partial bit-vector functions, such as
  \texttt{bvudiv}, or underspecified floating-point functions, such as
  \texttt{fp.min}, will be eligible for the competition again.
  \emph{Rationale:} A conclusion on the semantics of these functions
  has finally been reached, and the status of affected SMT-LIB
  benchmarks has been updated accordingly.
\item Benchmarks with unknown status will be eligible for the
  competition's main track.  In 2016, solver performance on benchmarks
  with unknown status was evaluated but reported separately; in 2017,
  it will directly affect the competition results.  \emph{Rationale:}
  Using only benchmarks with known status (i.e., benchmarks that have
  been solved before) to determine the competition results unjustly
  favors imitation of existing solvers over true innovation.
\item In the competition-wide scoring, the (per-division) penalty for
  erroneous results is changed from the number of errors to a fixed
  constant (multiplied by the weight of the respective division).
  \emph{Rationale:} The weight already takes the number of benchmarks
  in the division into account; multiplying it by the number of errors
  overemphasizes large divisions.
\item The unsat-core track, which was re-introduced in 2016, is no
  longer experimental.  Its divisions will be considered competitive
  if the necessary requirements (see Section~\ref{sec:scoring}) are
  met.  \emph{Rationale:} Rules and tool support for the unsat-core
  track proved sufficiently stable in 2016.
\item The competition will feature experimental divisions for
  benchmarks that use algebraic datatypes.  \emph{Rationale:}
  Algebraic datatypes are specified in the draft SMT-LIB~2.6 standard,
  which is expected to become official in the near future, and are
  already supported by some solvers.  Benchmarks that use datatypes
  have recently been added to SMT-LIB.
\end{itemize}
\rem{Aina: Are we going to introduce an experimental strings divisions?}

@@

For participation in SMT-COMP, a solver must be uploaded to StarExec
and made publicly available.  StarExec supports solver configurations;
for clarity, \emph{each submitted solver must have one configuration
  only}.  Moreover, the organizers must be informed of the solver's
presence \emph{and the tracks and divisions in which it is
  participating} via the web form at
\begin{center}
  \rem{TODO, this is still the old link: https://goo.gl/forms/HL6rbOywqW4sFo1D2}
  {\tt TBA}
\end{center}
A submission must also include a 32-bit unsigned integer.  These
integer numbers, collected from all submissions, are used to seed the
benchmark scrambler.

@@

\header{Main track: removal of disagreements.}
%
Before division scores are computed for the main track, benchmarks
with unknown status are removed from the competition results if two
(or more) solvers that are sound on benchmarks with known status
disagree on their result.  More specifically, a solver (including a
solver that was entered into the competition by the organizers for
comparison purposes) is \emph{sound on benchmarks with known status}
for a division if its raw score (Section~\ref{sec:benchmark-scoring})
is of the form $\langle 0, n, w, c\rangle$ for each benchmark in the
division, i.e., if it did not produce any erroneous results.  Two
solvers \emph{disagree} on a benchmark if one of them reported
\texttt{sat} and the other reported \texttt{unsat}.  Only the
remaining benchmarks are used in the following computation of division
scores (but the organizers may report disagreements for informational
purposes).
\rem{Aina: I strongly suggest that we make disagreements visible.  I
  would add a table to the bottom of the division results page, where
  we list the benchmarks we removed due to disagreements and which
  results which solvers reported. Silently dropping benchmarks on
  which solvers disagree is potentially unfair and dangerous, since
  people who want to use a solver, tend to only look at the SMT-COMP
  results and pick a solver based on this results.  They will
  certainly not go through the competition results on StarExec, in
  particular since this is quite tedious.  For users it is interesting
  (and might be actually crucial) to know if a solver disagreed with
  other solvers.  The same is true for solver developers, since they
  certainly want to know if their solver disagreed with other solvers
  on a certain benchmark.  They usually run preliminary tests with
  existing solvers beforehand, but not all solvers are available in
  the newest version.  Not to mention new solvers.}

@@

\rem{Aina: Do we already know how many medals FLOC is going to sponsor?
Clark offered to pay for printing proper and beautiful certificates for each
division if we don't have funds for that.
As for medals, it might be a little late to get sponsors (and the funds
from SMT-LIB went to the travel fund).}

\rem{Aina: Depending on the number of medals we get from FLOC we should
decide on how to categorize for prizes. Some ideas:
\begin{itemize}
  \item Competition-wide, main track, best solver
  \item Quantified divisions, best solver
  \item Either QF\_BV best solver, or QF\_BV + QF\_ABV + QF\_AUFBV + QF\_UFBV
  \item Competition-wide, application track, best solver
  \item Competition-wide, unsat-core track, best solver
  \item Best newcomer
\end{itemize}
Floating-point is currently only officially supported by Z3,
inofficially also by CVC4, if we expect more than 2 entrants, then FP logics
would also be a candidate.
}

@@

\header{Disclosure.}
%
Aina Niemetz is part of the developing teams of the SMT solvers
Boolector~\cite{boolector}
and CVC4~\cite{cvc4}.
Matthias Heizmann is associated with the group producing the
SMTInterpol~\cite{smtinterpol} solver.
Giles Reger is associated with the group
producing the Vampire system\rem{TODO for Giles: cite Vampire}~\cite{vampire}.

>>>>

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Matthias Heizmann, Albert Oliveras, Giles Reger, Aaron Stump, and
  Tjark Weber.}  describes the rules and competition procedures for
SMT-COMP~2018.  The principal changes from the previous competition
rules are the following:
\begin{itemize}
\item The organizers plan to recognize additional special
  contributions.  These might include:
  \begin{itemize}
  \item Best application track solver (awarded based on a
    competition-wide scoring for the application track)
  \item Best unsat-core track solver (awarded based on a
    competition-wide scoring for the unsat-core track)
  \item Best complementary solver (awarded to the solver that performs
    best when all benchmarks solved by the winning solver are removed)
  \item Most unique solver (awarded to the solver that performs best
    on benchmarks solved by only one solver)
  \item The Prophet (awarded to the solver that performs best on
    benchmarks with unknown status)
  \item The 10 Second Wonder (awarded to the solver that would have
    won if the time limit was 10 seconds)
  \end{itemize}
  The details are still being discussed and subject to change.
\item In the unsat-core track, the unsatisfiability check for the
  returned core will be based on a simple majority vote.  The case
  that a solver finds its own core satisfiable will no longer be
  treated specially.  \emph{Rationale:} This allows to simplify the
  post-processing of unsat-core track results considerably.

\item In 2017, the competition featured experimental divisions for
  benchmarks that use algebraic datatypes.  Provided the competition
  tools can be enhanced in time to support datatypes, these divisions
  may become regular (non-experimental) in 2018. \emph{Rationale:}
  Algebraic datatypes are specified in the latest official release
  (Version~2.6) of the SMT-LIB standard.

\item The competition may feature experimental divisions for
  benchmarks that use strings, and for benchmarks that use
  transcendental functions.  \emph{Rationale:} Corresponding theories
  and benchmarks are expected to be added to SMT-LIB in the near
  future.
\end{itemize}

@@

For participation in SMT-COMP, a solver must be uploaded to StarExec
and made publicly available.  StarExec supports solver configurations;
for clarity, \emph{each submitted solver must have one configuration
  only}.  Moreover, the organizers must be informed of the solver's
presence \emph{and the tracks and divisions in which it is
  participating} via the web form at
\begin{center}
  \rem{{\tt TBA}}
\end{center}
A submission must also include a 32-bit unsigned integer.  These
integer numbers, collected from all submissions, are used to seed the
benchmark scrambler.

@@

\header{Main track: removal of disagreements.}
%
Before division scores are computed for the main track, benchmarks
with unknown status are removed from the competition results if two
(or more) solvers that are sound on benchmarks with known status
disagree on their result.  More specifically, a solver (including a
solver that was entered into the competition by the organizers for
comparison purposes) is \emph{sound on benchmarks with known status}
for a division if its raw score (Section~\ref{sec:benchmark-scoring})
is of the form $\langle 0, n, w, c\rangle$ for each benchmark in the
division, i.e., if it did not produce any erroneous results.  Two
solvers \emph{disagree} on a benchmark if one of them reported
\texttt{sat} and the other reported \texttt{unsat}.  Only the
remaining benchmarks are used in the following computation of division
scores (but the organizers may report disagreements for informational
purposes).

@@

@@

\header{Disclosure.}
%
Aina Niemetz is part of the developing teams of the SMT solvers
Boolector~\cite{boolector}
and CVC4~\cite{cvc4}.
Matthias Heizmann is associated with the group producing the
SMTInterpol~\cite{smtinterpol} solver.
Giles Reger is associated with the group
producing the Vampire system~\cite{vampire}.
